\documentclass[letterpaper]{article}
\usepackage{calc}
\usepackage{xcolor}
\usepackage{xparse}
%\usepackage{textpos}
\usepackage[showboxes]{textpos} % DEBUG
\usepackage{setspace}
\usepackage{geometry}
\usepackage[fixed]{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage[nomessages]{fp}
\usepackage[utopia]{mathdesign}
\usepackage[pdfborder={0 0 0}]{hyperref}
\input{commands.tex}
\def\name{Albert Zang}
\def\motto{Keep it simple, code it right!}
\def\phone{\href{tel:+17782378615}{+1 (778) 237-8615}}
\def\email{\href{mailto:albertzang.ys@gmail.com}{albertzang.ys@gmail.com}}
\def\linkedin{\href{https://www.linkedin.com/in/albertzang/}{linkedin.com/in/albertzang}}
\def\home{\href{https://maps.app.goo.gl/5JedGP1KRUeaAWsi9}{Vancouver BC, Canada}}

\begin{document}
%\showgrid   % DEBUG
\grid*{60}{12}{60}{\hfill\fontxl\textbf{\textsc{\name}}}
\grid{60}{3}{0}{\fontsm\faIcon{phone} \phone}
\grid{60}{3}{0}{\fontsm\faIcon{at} \email}
\grid{60}{3}{0}{\fontsm\faIcon{linkedin-in} \linkedin}
\grid{60}{3}{0}{\fontsm\faIcon{home} \home}
\grid{120}{2}{0}{\rule{120\TPHorizModule}{0.5pt}}[][0pt]
%--------------------------------------------------------------------------------%
\spacer{1}
\grid{120}{4}{0}{\fontmd\faIcon{cogs} \textsc{Technical Vocabulary}}[lightgray]
\spacer{1}
%--------------------------------------------------------------------------------%
\grid{120}{12}{0}{\fontsm
    \textbf{[ Languages ]} $\cdot$
    C/C++ $\cdot$
    C\# $\cdot$
    CSS $\cdot$
    Go $\cdot$
    Java $\cdot$
    JavaScript $\cdot$
    Python $\cdot$
    Scala $\cdot$
    TypeScript $\cdot$
    \textbf{[ Frameworks ]} $\cdot$
    D3.js $\cdot$
    GraphQL $\cdot$
    gRPC $\cdot$
    Next.js $\cdot$
    Node.js $\cdot$
    Qt $\cdot$
    React $\cdot$
    REST $\cdot$
    Spark $\cdot$
    \textbf{[ Toolkits ]} $\cdot$
    Docker $\cdot$
    Git $\cdot$
    Kafka $\cdot$
    Kubernetes $\cdot$
    Linux $\cdot$
    Webpack $\cdot$
    \textbf{[ Databases ]} $\cdot$
    Cassandra $\cdot$
    MySQL $\cdot$
    PostgresSQL $\cdot$
    Redis $\cdot$
    \textbf{[ AI ]} $\cdot$
    LLM Agents $\cdot$
    OpenAI API $\cdot$
    Prompt Engineering $\cdot$
    RAG $\cdot$
    \textbf{[ Methodologies ]} $\cdot$
    Agile $\cdot$
    Big Data $\cdot$
    CI/CD $\cdot$
    Data Pipeline $\cdot$
    Data Visualization $\cdot$
    ETL $\cdot$
    Machine Learning $\cdot$
    Microservice $\cdot$
    Web Application
}


%--------------------------------------------------------------------------------%
\spacer{1}
\grid{120}{4}{0}{\fontmd\faIcon{suitcase} \textsc{Work Experience}}[lightgray]
\spacer{1}
%--------------------------------------------------------------------------------%
%--------------------------------------------------------------------------------%
\grid{120}{4}{0}{\fontmd\underline{Microsoft $\cdot$ Senior Software Engineer}
\hfill\fontxs{Vancouver, Canada $\cdot$ Jun 2024 - Present}}
%--------------------------------------------------------------------------------%
\grid{120}{9}{0}{\fontsm
Actively engaged in productizing the Copilot prototype for AI infrastructure, working
closely with the Microsoft Research team. Acquiring extensive hands-on experience with
Azure OpenAI APIs, prompt engineering, Retrieval-Augmented Generation (RAG), and Large
Language Model (LLM)-based agents development.
}
%--------------------------------------------------------------------------------%
\grid{120}{4}{0}{\fontmd\underline{Salesforce $\cdot$ Lead MTS} \fontxs\textsl{Promotion}
\hfill\fontxs{Vancouver, Canada $\cdot$ Feb 2022 - Dec 2023}}
%--------------------------------------------------------------------------------%
\grid{120}{15}{0}{\fontsm
As a Technical Lead, contributed to collaborative decision-making and problem-solving
through participation in cross-team architectural design discussions. Spearheaded the
technical design and implementation of the Explain Data service's gRPC API. Addressed
escalating on-call backlog by implementing a scheduled incident monitoring dashboard
using Splunk, significantly decreased our incident response time. Effectively managed
technical challenges by evaluating trade-offs, prioritizing development, making decisions,
and resolving problems. Highly valued by peers for mentorship on challenging topics,
actively enhancing team capabilities and advancing team members' careers.
}
%--------------------------------------------------------------------------------%
\grid{120}{4}{0}{\fontmd\underline{Salesforce $\cdot$ Senior MTS} \fontxs\textsl{Acquisition $\cdot$ Promotion}
\hfill\fontxs{Vancouver, Canada $\cdot$ Apr 2020 - Jan 2022}}
%--------------------------------------------------------------------------------%
\grid{120}{18}{0}{\fontsm
As a Scrum Master, I effectively organized team priorities and facilitated meetings,
steering the team through major transitions including a management change and the
shift to remote work, ensuring seamless operations. Led the design, implementation,
and testing of the telemetry project for Explain Data in collaboration with user
research and telemetry infrastructure team. This effort resulted in a comprehensive
dashboard that tracks feature usage and adoption, providing essential insights for
strategic decisions and data-driven improvements. Earned a prestigious role in
Tableau's Browser Community of Practice (BCoP) through recognized contributions in
the company-wide web development spacer, serving as Community Organizer and hosting
monthly Tableau web development community meetings.
}
%--------------------------------------------------------------------------------%
\grid{120}{4}{0}{\fontmd\underline{Tableau $\cdot$ Software Engineer}
\hfill\fontxs{Vancouver, Canada $\cdot$ May 2018 - Mar 2020}}
%--------------------------------------------------------------------------------%
\grid{120}{15}{0}{\fontsm
Played a major role in the UI development of the Explain Data feature and became
the team's primary contact for UI-related issues. Extended Tableau's module-dev-scripts
to bundle UI modules into a static site on GitLab Pages, integrating with our CI/CD
pipeline. This pivotal innovation expedited cross-functional feedback, significantly
speeding up the development process and fostering seamless innovation across teams.
Spearheaded key enhancements to Tableau's Hybrid UI framework, including making
the Hybrid Dialog resizable and adding a Hybrid Side Panel, enhancing functionality
across feature teams and supporting Tableau's product success.
}
%--------------------------------------------------------------------------------%
\grid{120}{4}{0}{\fontmd\underline{Fortinet $\cdot$ Web Developer}
\hfill\fontxs{Burnaby, Canada $\cdot$ May 2013 - Jun 2015}}
%--------------------------------------------------------------------------------%
\grid{120}{15}{0}{\fontsm
Skilled in developing rich web applications using AngularJS, jQuery, Bootstrap,
and Django, demonstrating expertise in full stack web development. Designed and
implemented modular components to improve scalability and maintainability of the
codebase. Developed dynamic and responsive web forms that accurately mirrored the
backend business object model and validated user inputs, enhancing user experience.
Developed data visualization widgets using D3.js to effectively communicate complex
data insights to end-users. Worked closely with product, design, and development
teams to deliver intuitive and feature-rich web applications.
}


%--------------------------------------------------------------------------------%
\spacer{1}
\grid{120}{4}{0}{\fontmd\faIcon{graduation-cap} \textsc{Education}}[lightgray]
\spacer{1}
%--------------------------------------------------------------------------------%
\grid{120}{3}{0}{\fontsm\underline{Professional Master's Program in Big Data}}
\grid{120}{3}{0}{\fontsm\textbf{Simon Fraser University}\hfill\fontxs{Burnaby, Canada}}
\grid{120}{3}{0}{\fontxs\textsl{M.Sc. in Computing Science}\hfill{Sep 2015 - Dec 2016}}
\grid{120}{3}{0}{\fontsm\underline{Dual-Degree Program in Computing Science}}
\grid{120}{3}{0}{\fontsm\textbf{Simon Fraser University}\hfill\fontxs{Burnaby, Canada}}
\grid{120}{3}{0}{\fontxs\textsl{B.Sc. in Computing Science}\hfill{Sep 2010 - Apr 2013}}
\grid{120}{3}{0}{\fontsm\textbf{Zhejiang University}\hfill\fontxs{Hangzhou, China}}
\grid{120}{3}{0}{\fontxs\textsl{B.Eng. in Computer Science and Technology}\hfill{Sep 2008 - Aug 2010}}
\end{document}