\documentclass[letterpaper]{article}
\usepackage{calc}
\usepackage{xcolor}
\usepackage{xparse}
\usepackage{textpos}
%\usepackage[showboxes]{textpos} % DEBUG
\usepackage{setspace}
\usepackage{geometry}
\usepackage[fixed]{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage[nomessages]{fp}
\usepackage[utopia]{mathdesign}
\usepackage[pdfborder={0 0 0}]{hyperref}
\input{commands.tex}
\def\name{Albert Zang}
\def\motto{Keep it simple, code it right!}
\def\phone{\href{tel:+17782378615}{(+1)778.237.8615}}
\def\email{\href{mailto:albertzang.ys@gmail.com}{albertzang.ys@gmail.com}}
\def\linkedin{\href{https://www.linkedin.com/in/albertzang/}{linkedin.com/in/albertzang}}
\def\home{\href{https://maps.app.goo.gl/5JedGP1KRUeaAWsi9}{Vancouver BC, Canada}}

\begin{document}
%\TPShowGrid{2}{160} % DEBUG
\headerfull{\name}{\motto}{\phone}{\email}{\linkedin}{\home}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectiontitle{cogs}{Technical Vocabulary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\gridpar{9}{
    \textbf{[ Languages ]} $\cdot$
    C/C++ $\cdot$
    C\# $\cdot$
    CSS $\cdot$
    Go $\cdot$
    Java $\cdot$
    JavaScript $\cdot$
    Python $\cdot$
    Scala $\cdot$
    TypeScript $\cdot$
    \textbf{[ Frameworks ]} $\cdot$
    D3.js $\cdot$
    GraphQL $\cdot$
    gRPC $\cdot$
    Next.js $\cdot$
    Node.js $\cdot$
    Qt $\cdot$
    React $\cdot$
    REST $\cdot$
    Spark $\cdot$
    \textbf{[ Toolkits ]} $\cdot$
    Docker $\cdot$
    Git $\cdot$
    Kafka $\cdot$
    Kubernetes $\cdot$
    Linux $\cdot$
    Webpack $\cdot$
    \textbf{[ Databases ]} $\cdot$
    Cassandra $\cdot$
    MySQL $\cdot$
    PostgresSQL $\cdot$
    Redis $\cdot$
    \textbf{[ Methodologies ]} $\cdot$
    Agile $\cdot$
    Big Data $\cdot$
    CI/CD $\cdot$
    Data Pipeline $\cdot$
    Data Visualization $\cdot$
    ETL $\cdot$
    Machine Learning $\cdot$
    Microservice $\cdot$
    Web Application
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectiontitle{suitcase}{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectiontitle{Salesforce $\cdot$ Lead Member of Technical Staff}
[Promotion][Vancouver, Canada $\cdot$ Feb 2022 - Dec 2023]
\gridpar{15}{
As a Technical Lead, contributed to collaborative decision-making and problem-solving
through participation in cross-team architectural design discussions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Spearheaded the technical design and implementation of the Explain Data service's
gRPC API.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Addressed escalating on-call backlog by implementing a scheduled incident monitoring
dashboard using Splunk, significantly decreased our incident response time.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Effectively managed technical challenges by evaluating trade-offs, prioritizing
development, making decisions, and resolving problems.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Highly valued by peers for mentorship on challenging topics, actively enhancing
team capabilities and advancing team members' careers.
}
\subsectiontitle{Salesforce $\cdot$ Senior Member of Technical Staff}
[Acquisition $\cdot$ Promotion][Vancouver, Canada $\cdot$ Apr 2020 - Jan 2022]
\gridpar{18}{
As a Scrum Master, I effectively organized team priorities and facilitated meetings,
steering the team through major transitions including a management change and the
shift to remote work, ensuring seamless operations.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Led the design, implementation, and testing of the telemetry project for Explain
Data in collaboration with user research and telemetry infrastructure team. This
effort resulted in a comprehensive dashboard that tracks feature usage and adoption,
providing essential insights for strategic decisions and data-driven improvements.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Earned a prestigious role in Tableau's Browser Community of Practice (BCoP) through
recognized contributions in the company-wide web development space, serving as
Community Organizer and hosting monthly Tableau web development community meetings.
}
\subsectiontitle{Tableau $\cdot$ Software Engineer}
[][Vancouver, Canada $\cdot$ May 2018 - Mar 2020]
\gridpar{15}{
Played a major role in the UI development of the Explain Data feature and became
the team's primary contact for UI-related issues.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Extended Tableau's module-dev-scripts to bundle UI modules into a static site on
GitLab Pages, integrating with our CI/CD pipeline. This pivotal innovation expedited
cross-functional feedback, significantly speeding up the development process and
fostering seamless innovation across teams.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Spearheaded key enhancements to Tableau’s Hybrid UI framework, including making
the Hybrid Dialog resizable and adding a Hybrid Side Panel, enhancing functionality
across feature teams and supporting Tableau’s product success.
}
\subsectiontitle{Alibaba $\cdot$ Senior Machine Learning Engineer}
[][Shanghai, China $\cdot$ Mar 2017 - Nov 2017]
\gridpar{15}{
Maintained a high-performance CTR prediction system using Spark, Hive, Kafka, and
Redis.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Built a feature engineering library to process billions of data records efficiently. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Trained prediction models using logistic regression, feature crossing, and
factorization machines.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Utilized Spark transformations and actions for batch and real-time processing.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Led performance optimization efforts through memory tuning, data persistence,
and variable broadcasting.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Collaborated with data infrastructure teams to successfully integrate the
prediction system into the overall data pipeline.
}
\subsectiontitle{Fortinet $\cdot$ Web Developer}
[][Burnaby, Canada $\cdot$ May 2013 - Jun 2015]
\gridpar{15}{
Skilled in developing rich web applications using AngularJS, jQuery, Bootstrap,
and Django, demonstrating expertise in full stack web development.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Designed and implemented modular components to improve scalability and
maintainability of the codebase.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Developed dynamic and responsive web forms that accurately mirrored the backend
business object model and validated user inputs, enhancing user experience.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Developed data visualization widgets using D3.js to effectively communicate
complex data insights to end-users.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Worked closely with product, design, and development teams to deliver intuitive
and feature-rich web applications.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectiontitle{graduation-cap}{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectiontitle{Professional Master's Program in Big Data}
\degree{Simon Fraser University}{M.Sc. in Computing Science}{Burnaby, Canada}{Sep 2015 - Dec 2016}
\subsectiontitle{Dual-Degree Program in Computing Science}
\degree{Simon Fraser University}{B.Sc. in Computing Science}{Burnaby, Canada}{Sep 2010 - Apr 2013}
\degree{Zhejiang University}{B.Eng. in Computer Science and Technology}{Hangzhou, China}{Sep 2008 - Aug 2010}
\end{document}
